% APPENDIX: EXPERIMENT CONFIGURATIONS
% AUTO-GENERATED from experiments/paper/*.yaml
% Last updated: 2026-02-19

This appendix summarizes all experiment configurations used in this paper.
Full YAML configs are available in the repository under \texttt{experiments/paper/}.

\begin{table}[htbp]
\centering
\caption{Experiment suite summary}
\label{tab:app-configs}
\small
\begin{tabular}{@{}lllrr@{}}
\toprule
ID & Name & Swept Parameters & Configs & Runs/Config \\
\midrule
00 & Baseline & (none) & 1 & 100 \\
01 & Calibration & participation targets & $3\times3=9$ & 100 \\
03 & Quorum Sensitivity & quorumPercentage & 5 & 100 \\
04 & Governance Capture & mitigation grid & 24 & 100 \\
05 & Proposal Pipeline & pipeline grid & 9 & 100 \\
06 & Treasury Resilience & treasury grid & 12 & 100 \\
07 & Inter-DAO & scenarios & 5 & 100 \\
08 & Scale Sweep & totalMembers & 5 & 100 \\
09 & Voting Mechanisms & mechanism $\times$ quorum & 6 & 100 \\
10 & Calibration Validation & DAO-specific profiles & 14 & 30 \\
11 & Advanced Mechanisms & mechanism (zip) & 4 & 100 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Key Parameter Ranges}

\begin{description}
    \item[00 Baseline] Default compound template, 200 members, 720 steps.
    \item[01 Calibration] Grid: \texttt{voting\_activity} $\in \{0.05, 0.15, 0.25\}$, \texttt{participation\_\allowbreak{}target\_rate} $\in \{0.1, 0.2, 0.3\}$.
    \item[03 Quorum Sensitivity] \texttt{quorumPercentage} $\in \{0.01, 0.05, 0.10, 0.20, 0.50\}$.
    \item[04 Governance Capture] Grid over vote power cap fraction, quadratic threshold, and velocity penalty.
    \item[05 Proposal Pipeline] Grid over temp-check fraction, fast-track settings, and inactivity expiry.
    \item[06 Treasury Resilience] Grid over buffer fraction, stabilization enabled/disabled, and max spend fraction.
    \item[07 Inter-DAO] Five scenarios: homogeneous, heterogeneous, asymmetric, specialized, and isolated.
    \item[08 Scale Sweep] \texttt{totalMembers} $\in \{50, 100, 200, 350, 500\}$.
    \item[09 Voting Mechanisms] Grid: governance rule $\in \{\text{majority, quadratic, conviction}\}$ $\times$ quorum $\in \{0.04, 0.08\}$.
    \item[10 Calibration Validation] Per-DAO profiles for 14 real-world DAOs (Uniswap, Compound, Aave, MakerDAO, ENS, Gitcoin, Hop, Arbitrum, Lido, Optimism, Nouns, Balancer, dYdX, SushiSwap), validating simulator accuracy against historical governance data.
    \item[11 Advanced Mechanisms] Zip sweep: governance rule $\in \{\text{majority, instant-runoff, futarchy}\}$ with matching voting strategy; includes enhanced liquid democracy (depth limit, decay).
\end{description}
