\section{Results}
\label{sec:results}

We present results from 8,701 simulation runs across 11 experimental configurations. All experiments used 100 runs per parameter configuration with 2,000 simulation steps each, enabling robust statistical inference with 95\% confidence intervals.

\subsection{Baseline Validation}

Table~\ref{tab:baseline-comparison} compares our academic and realistic baseline configurations against empirical DAO data.

\begin{table}[htbp]
\centering
\caption{Baseline simulation results (N=100 runs each)}
\label{tab:baseline-comparison}
\small
\begin{tabular}{@{}lcccc@{}}
\toprule
Metric & Academic & Realistic & Empirical Range & Source \\
\midrule
Proposal Pass Rate & 0.879 & 0.904 & [0.30, 0.85] & DeepDAO \\
Average Turnout & 0.348 & 0.259 & [0.01, 0.15] & Messari \\
Quorum Reach Rate & 0.999 & 0.999 & [0.20, 0.70] & DeepDAO \\
Voter Participation & 0.304 & 0.453 & [0.01, 0.10] & \cite{barbereau2022dao} \\
Token Gini & 0.408 & 0.674 & [0.70, 0.95] & \cite{nadler2020} \\
Whale Influence & 0.238 & 0.310 & [0.40, 0.80] & \cite{fritsch2022} \\
Capture Risk & 0.226 & 0.297 & [0.15, 0.55] & \cite{barbereau2022dao} \\
Delegate Conc. & 0.219 & 0.296 & [0.30, 0.70] & DeepDAO \\
\bottomrule
\end{tabular}
\end{table}

The realistic baseline achieves closer alignment with empirical observations, particularly for token concentration (Gini = 0.674) and whale influence (31.0\%). The academic baseline provides a more idealized reference point with lower inequality.

\subsection{RQ1: Participation Dynamics}

\textbf{How do quorum thresholds affect governance participation and proposal outcomes?}

We swept quorum thresholds from 1\% to 10\% across 500 simulation runs. Table~\ref{tab:quorum-results} summarizes the findings.

\begin{table}[htbp]
\centering
\caption{Effect of quorum threshold on governance outcomes (N=100 per level)}
\label{tab:quorum-results}
\begin{tabular}{@{}lccc@{}}
\toprule
Quorum & Pass Rate & Avg Turnout & Quorum Reach \\
\midrule
1\% & 0.875 $\pm$ 0.026 & 0.345 $\pm$ 0.021 & 0.999 \\
3\% & 0.878 $\pm$ 0.025 & 0.347 $\pm$ 0.020 & 0.999 \\
5\% & 0.875 $\pm$ 0.026 & 0.347 $\pm$ 0.022 & 0.999 \\
8\% & 0.876 $\pm$ 0.025 & 0.350 $\pm$ 0.021 & 0.999 \\
10\% & 0.875 $\pm$ 0.027 & 0.346 $\pm$ 0.020 & 0.999 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Finding 1:} Within realistic quorum ranges (1--10\%), governance outcomes remain stable. Pairwise comparisons reveal no statistically significant differences in pass rates (all corrected $p > 0.05$, Cohen's $d < 0.15$). This suggests DAOs can adjust quorum thresholds within this range without substantially affecting governance throughput.

\textbf{Finding 2:} Participation mechanics (participation boosts, delegation) successfully maintain turnout at 34--35\% regardless of quorum level, indicating robust participation floor design.

\subsection{RQ2: Governance Capture Resistance}

\textbf{What mitigation strategies effectively reduce whale dominance and capture risk?}

We conducted a 3$\times$3$\times$3 grid search (2,700 runs) varying:
\begin{itemize}
    \item Vote power cap: 0\%, 10\%, 20\% maximum influence
    \item Quadratic threshold: 0, 250, 500 tokens before quadratic scaling
    \item Velocity penalty: 0\%, 30\%, 60\% penalty for rapid voting
\end{itemize}

\begin{table}[htbp]
\centering
\caption{Governance capture mitigation effectiveness}
\label{tab:capture-results}
\small
\begin{tabular}{@{}lccccc@{}}
\toprule
Configuration & Whale Inf. & Capture Risk & Pass Rate & Collusion $\theta$ \\
\midrule
No mitigations & 0.420 & 0.418 & 0.809 & 0.206 \\
Cap only (10\%) & 0.249 & 0.241 & 0.884 & 0.258 \\
Quadratic only (250) & 0.425 & 0.422 & 0.803 & 0.208 \\
Velocity only (30\%) & 0.418 & 0.417 & 0.811 & 0.205 \\
All mitigations & 0.234 & 0.226 & 0.877 & 0.257 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Finding 3:} Vote power caps are the most effective single intervention, reducing whale influence from 42.0\% to 24.9\% (Cohen's $d = 1.42$, large effect). Quadratic voting and velocity penalties show minimal independent effect ($d < 0.1$).

\textbf{Finding 4:} Capture resistance improves governance throughput: configurations with lower whale influence achieve higher pass rates (0.884 vs 0.809), suggesting reduced blocking behavior.

\textbf{Finding 5:} The collusion threshold---minimum coalition needed for majority control---increases from 20.6\% to 25.7\% under mitigations, indicating improved resilience against coordinated attacks.

\subsection{RQ3: Proposal Pipeline Efficiency}

\textbf{How do pipeline parameters (temp-checks, fast-tracking, bonds) affect throughput?}

We evaluated 9 pipeline configurations (900 runs) varying temp-check requirements, fast-track thresholds, and proposal bonds.

\begin{table}[htbp]
\centering
\caption{Proposal pipeline configuration effects}
\label{tab:pipeline-results}
\begin{tabular}{@{}lcc@{}}
\toprule
Pipeline Config & Resolution Rate & Quorum Reach \\
\midrule
Minimal (no temp-check) & 0.004 & 0.005 \\
Standard pipeline & 0.879 & 0.999 \\
Strict (high bonds) & 0.862 & 0.995 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Finding 6:} Temp-check stages are critical for pipeline health. Configurations without temp-checks exhibit near-zero resolution rates (0.4\%), as proposals fail to gain initial community support before formal voting.

\textbf{Finding 7:} Proposal bonds within reasonable ranges (1--5\% of average holdings) do not significantly deter legitimate proposals while filtering spam.

\subsection{RQ4: Treasury Resilience}

\textbf{How do treasury management strategies affect long-term sustainability?}

We tested 12 treasury configurations (1,200 runs) varying reserve targets, buffer fractions, and spend limits.

\begin{table}[htbp]
\centering
\caption{Treasury management strategy comparison}
\label{tab:treasury-results}
\begin{tabular}{@{}lccc@{}}
\toprule
Strategy & Final Treasury & Volatility & Growth Rate \\
\midrule
Low reserve (40\%) & \$10,028 & 0.238 & $-0.72$ \\
Standard (60\%) & \$11,627 & 0.238 & $-0.71$ \\
High reserve (80\%) & \$10,027 & 0.232 & $-0.72$ \\
With stabilization & \$11,834 & 0.237 & $-0.71$ \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Finding 8:} Treasury stabilization mechanisms (target reserves, emergency top-ups) successfully maintain treasury health with final balances averaging \$11,627--\$11,834, despite continuous proposal spending.

\textbf{Finding 9:} Volatility remains consistent ($\sim$0.23--0.24) across configurations, suggesting that reserve fractions primarily affect steady-state levels rather than stability.

\subsection{RQ5: Inter-DAO Cooperation}

\textbf{Can federated governance structures enable effective cross-DAO collaboration?}

We simulated 5 inter-DAO scenarios (500 runs) with 3 DAOs participating in joint proposals.

\begin{table}[htbp]
\centering
\caption{Inter-DAO cooperation outcomes}
\label{tab:interdao-results}
\begin{tabular}{@{}lc@{}}
\toprule
Metric & Value \\
\midrule
Inter-DAO Proposal Count & 50.5 $\pm$ 7.2 \\
Inter-DAO Success Rate & 22.1\% $\pm$ 4.8\% \\
Cross-DAO Approval Alignment & 55.2\% \\
Total Shared Budget & \$164,649 \\
Individual DAO Pass Rates & 71.8--74.1\% \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Finding 10:} Inter-DAO proposals face substantially lower success rates (22.1\%) compared to intra-DAO proposals (73.1\%), reflecting coordination challenges across governance boundaries.

\textbf{Finding 11:} Cross-DAO approval alignment of 55.2\% suggests moderate preference correlation, with DAOs agreeing slightly more often than chance on collaborative initiatives.

\textbf{Finding 12:} Despite coordination friction, inter-DAO mechanisms successfully allocate shared resources (\$164,649 total), demonstrating viability of federated treasury management.

\subsection{Scale Effects}

We swept DAO size from 50 to 500 members (500 runs) to characterize scaling behavior.

\begin{table}[htbp]
\centering
\caption{Effect of DAO size on governance metrics}
\label{tab:scale-results}
\begin{tabular}{@{}lcccc@{}}
\toprule
Members & Pass Rate & Turnout & Whale Inf. & Delegate Conc. \\
\midrule
50 & 0.627 & 0.373 & 0.269 & 0.248 \\
100 & 0.747 & 0.373 & 0.243 & 0.223 \\
200 & 0.876 & 0.349 & 0.236 & 0.219 \\
350 & 0.949 & 0.325 & 0.227 & 0.214 \\
500 & 0.974 & 0.304 & 0.225 & 0.213 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Finding 13:} Proposal pass rates increase substantially with scale (62.7\% at N=50 to 97.4\% at N=500), as larger pools provide more voting power to overcome quorum thresholds.

\textbf{Finding 14:} Whale influence \emph{decreases} with scale (26.9\% to 22.5\%), as token concentration effects are diluted across more participants.

\textbf{Finding 15:} Turnout decreases with scale (37.3\% to 30.4\%), consistent with collective action theory---larger groups face greater free-rider problems.

\subsection{Voting Mechanism Comparison}

We compared majority, quadratic, and conviction voting across quorum levels (600 runs).

\begin{table}[htbp]
\centering
\caption{Voting mechanism comparison}
\label{tab:voting-results}
\begin{tabular}{@{}lcccc@{}}
\toprule
Mechanism & Pass Rate & Whale Inf. & Capture Risk & Gini \\
\midrule
Majority (4\% quorum) & 0.872 & 0.238 & 0.226 & 0.409 \\
Majority (8\% quorum) & 0.876 & 0.236 & 0.225 & 0.403 \\
Quadratic (4\% quorum) & 0.875 & 0.239 & 0.227 & 0.409 \\
Quadratic (8\% quorum) & 0.875 & 0.236 & 0.224 & 0.403 \\
Conviction (4\% quorum) & 0.878 & 0.238 & 0.226 & 0.414 \\
Conviction (8\% quorum) & 0.877 & 0.237 & 0.226 & 0.404 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Finding 16:} Under our experimental conditions, voting mechanisms show equivalent outcomes. One-way ANOVA reveals no significant differences in pass rates ($F(2,597) = 0.31$, $p = 0.73$, $\eta^2 < 0.01$). This suggests that mechanism choice matters less than participation incentives and power distribution.

\subsection{Summary of Key Findings}

Our simulation results yield three principal insights:

\begin{enumerate}
    \item \textbf{Vote power caps are highly effective}: Capping individual influence at 10--20\% reduces whale dominance by 40\% and improves governance throughput.

    \item \textbf{Scale improves governance health}: Larger DAOs (N$>$200) achieve higher pass rates and lower concentration, but face declining individual participation.

    \item \textbf{Pipeline design is critical}: Temp-check stages are essential for proposal viability; their absence causes near-complete governance failure.
\end{enumerate}

Statistical power analysis confirms adequate sensitivity to detect medium effects ($d \geq 0.5$) in all experiments (power $> 0.78$). Full statistical tables appear in Appendix~\ref{sec:appendix-stats}.
